---
title: "Linstat Rec 1"
author: "Frederick Nilsen"
date: "21.01.2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1
### a)

```{r}
A <- matrix(c(9,-2,-2,6),nrow=2,ncol=2)
print(A)
```

### b)

```{r}
print(A-t(A))
```

We see that the difference between $A$ and its transposed is the ($2\times2$) zero matrix. Thus, $A$ is symmetric. This is also easily verifiable by hand, since $A^T$ would be
$$
\left[
\begin{matrix}
9 & -2 \\
-2 & 6
\end{matrix}
\right],
$$
which is the same as $A$.

### c)

To find out if $A$ is positive definite, we check if $A$ is diagonal-dominant. From **a)**, we see that its diagonals, $9$ and $6$, are both positive and greater than the absolute value of non-diagonal entries, $|-2|$. Hence, $A$ is positive definite.

### d)
By hand, we solve the system
$$
\text{det}(A-\lambda I)=0\iff (9-\lambda)(6-\lambda)-4=0
$$
for $\lambda$, which simply factors to $(\lambda-10)(\lambda-5)$. In R, we use `eigen()`:

```{r}
tmp <- eigen(A)
eVecs <- tmp$vectors
eVals <- tmp$values
print(eVecs)
```
```{r}
print(eVals)
```
### e)
We already have all we need to find the orthogonal diagonalization $A=V \Lambda V^{-1}$, we simply need to find the eigenvector matrix's inverse (using `solve()`) and $\Lambda$ using $\texttt{diag(}\lambda\texttt{)}$
```{r}
eVecsInv <- solve(eVecs)
Lmbd <- diag(eVals)
print(eVecs%*%Lmbd%*%eVecsInv)
```

### f)
```{r}
A_inv <- solve(A)
```

### g)
```{r}
print(eigen(A_inv))
```

The relationship between $\lambda(A)$ and $\lambda(A{-1})$ is clearly that $\lambda(A^{-1})=1/\lambda(A)$, i.e. $\frac15$ and $\frac{1}{10}$. As a consequence, the eigenvectors, which can freely be scaled, will be the same.

### h)
We've seen in the lectures that a covariance matrix must be symmetric and positive semi-definite. We've already shown that it's symmetric, and that it's positive defininte, thus it can represent some covariance matrix.

### i)

```{r}
corrMatrix <- rbind(c(0,0), c(0,0))
for (i in 1:nrow(A)){
    for (j in 1:ncol(A)){
        corrMatrix[i,j] = A[i,j]/sqrt(A[i,i]*A[j,j])
    }
}
print(corrMatrix)
```
Check with built-in function:
```{r}
print(cov2cor(A))
```
### j)
