---
title: "Compulsory assignment 1 [unfinished!]"
author: "Frederick Nilsen"
date: "23 1 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
## a)
We first determine $\pmb{\mu_Y}$. Since $E(A \mathbf{X})=A E\mathbf{X}$, we have
$$
\pmb{\mu_Y}:=E\mathbf{Y}=
\left(
\begin{matrix}
1/\sqrt{2} & -1/\sqrt{2} \\
1/\sqrt{2} & 1/\sqrt{2}
\end{matrix}
\right)
\left(
\begin{matrix}
0 \\ 2
\end{matrix}
\right)=
\left(
\begin{matrix}
-\sqrt{2} \\ \sqrt{2}
\end{matrix}
\right)
$$
To find the covariance matrix $\Sigma$, we use the property that $\text{Cov}(A\mathbf{X})=A \text{Cov}\mathbf{X}A^T$. We calculate this in R:

```{r}
pr1_A <- matrix(c(1/sqrt(2), -1/sqrt(2), 1/sqrt(2), 1/sqrt(2)), nrow=2, byrow=TRUE)
pr1_Sigma_X <- rbind(c(3,1), c(1,3))
pr1_Sigma_Y <- pr1_A %*% pr1_Sigma_X %*% t(pr1_A)
pr1_Sigma_Y
```
We thus define our covariance matric $\Sigma_Y$ to be
$$
\Sigma_Y=
\left(
\begin{matrix}
2 & 0 \\ 0 & 4
\end{matrix}
\right).
$$
The random variable $\mathbf{Y}$ has a bivariate normal distribution, since it is a linear combination of the bivariate normal distribution $\mathbf{X}$. From $\Sigma_Y$, we also see that $\text{Cov}(Y_1, Y_2)=0$, hence the variables are independent.

## b)

A little stuck on this





```{r pressure, echo=FALSE}
plot(pressure)
```
Det plottet er bare for å vise echo false.